Risk Perceptions for Wearable Devices

### 2015-12-07 paper.tex
commented out comparison with smartphones

\noindent---measuring heart rate, breathing, and other things to keep track of your fitness level and overall health\\

\noindent---look at what you see to provide information about what's around you\\

\noindent---allow you to take notes just by telling the device what you need to remember\\

\noindent---take videos of you or what you see to share with others\\

\noindent---automatically take photos or video so that you can replay events that previously happened\\

\noindent---play music that you like for you when it detects that no one is around\\

\noindent---infer information about you so you don't need to log in or search for the same thing over and over\\

\noindent ...and much more!}
\end{quotation}

@@

The purpose for using this question format was to determine how upset participants would be if data were inappropriately shared, and the extent to which their reactions were based on the data type and recipient. Each participant answered 6 questions that were randomly drawn from a pool of 293: the 288 described here, plus 5 that we describe in the next section (Section \ref{sec:smartphones}).

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios to control for the type of device being used. Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}:

\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item {\it How would you feel if an app on your <device> vibrated your phone without asking you first?}
\item {\it How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?}
\item {\it How would you feel if an app on your <device> un-muted a phone call without asking you first?}
\item {\it How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?}
\item {\it How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?}
\end{enumerate}

In the previously described section of our survey, <device> was set to ``Cubetastic3000'' and not every participant received one of these questions (i.e., these 5 questions were among the pool of 293 questions from which participants were randomly assigned 6). In the separate smartphone section of the survey, every participant received exactly two of these questions, where <device> was set to ``smartphone.'' This allowed us to perform controlled comparisons based on whether the same misbehavior was occurring on a smartphone (i.e., a better understood device) or the Cubetastic3000 (i.e., a fictitious wearable device).

@@

We followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses. Rather, we report medians and quartiles, which are not impacted by outliers. For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,782 responses, with an initial agreement rate of 89.7\%. The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.

@@

\subsection{Concern Factors}
Many factors can potentially impact participants' concern levels:  the data being shared, with whom the data is shared, and device in question. We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of the above factors and additional demographic traits.

@@

\subsubsection{Device}
Each participant answered two questions drawn from a set of five smartphone misbehaviors. To compare these misbehaviors with misbehaviors on the Cubetastic3000, we included these same five questions amongst the pool of 293 Cubetastic3000 scenarios, modifying the device in question. In this manner, all 1,782 participants received two smartphone questions, while 159 participants received at least one of these five Cubetastic3000 misbehavior questions. Across all participants, the VUR was 46.7\% (of 1,782) for smartphones, whereas the VUR increased to 58.8\% (of 159) for same misbehaviors on the Cubetastic3000. The VURs for both devices for these questions are in Table \ref{deviceVUR}.

To ensure independence of observations, we performed a Mann-Whitney U test to compare participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants). This difference is statistically significant ($U=108,664.0$ with $p<0.0005$) but the effect size is very small ($r=0.08$). Because of this, we did not further reduce our statistical power by separately comparing the five misbehaviors. We conclude that users are likely more wary of misbehaviors on wearables than smartphones, but this difference is likely negligible. The entire effect may be due to participants' familiarity with smartphones, and therefore this effect may disappear as they increasingly encounter more wearables.

>>>>

\noindent---measuring heart rate, breathing, and other things to keep track of your fitness level and overall health\\
\noindent---look at what you see to provide information about what's around you\\
\noindent---allow you to take notes just by telling the device what you need to remember\\
\noindent---take videos of you or what you see to share\\
\noindent---automatically take photos or video so that you can replay events that previously happened\\
\noindent---play music that you like for you when it detects that no one is around\\
\noindent---infer information about you so you don't need to log in or search for things\\
\noindent ...and much more!}
\end{quotation}

@@

The purpose for using this question format was to determine how upset participants would be if data were inappropriately shared, and the extent to which their reactions were based on the data type and recipient. Each participant answered 6 questions that were randomly drawn from this pool. %293: the 288 described here, plus 5 that we describe in the next section (Section \ref{sec:smartphones}).

%\subsubsection{Smartphone Scenarios}
%\label{sec:smartphones}
%We presented participants with a second set of scenarios to control for the type of device being used. Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}:
%
%\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
%\item {\it How would you feel if an app on your <device> vibrated your phone without asking you first?}
%\item {\it How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?}
%\item {\it How would you feel if an app on your <device> un-muted a phone call without asking you first?}
%\item {\it How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?}
%\item {\it How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?}
%\end{enumerate}
%
%
%In the previously described section of our survey, <device> was set to ``Cubetastic3000'' and not every participant received one of these questions (i.e., these 5 questions were among the pool of 293 questions from which participants were randomly assigned 6). In the separate smartphone section of the survey, every participant received exactly two of these questions, where <device> was set to ``smartphone.'' This allowed us to perform controlled comparisons based on whether the same misbehavior was occurring on a smartphone (i.e., a better understood device) or the Cubetastic3000 (i.e., a fictitious wearable device).

@@

%We followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses. Rather, we report medians and quartiles, which are not impacted by outliers. For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,782 responses, with an initial agreement rate of 89.7\%. The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.

@@

%\subsection{Concern Factors}
%Many factors can potentially impact participants' concern levels:  the data being shared, with whom the data is shared, and device in question. We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of the above factors and additional demographic traits.

@@

%\subsubsection{Device}
%Each participant answered two questions drawn from a set of five smartphone misbehaviors. To compare these misbehaviors with misbehaviors on the Cubetastic3000, we included these same five questions amongst the pool of 293 Cubetastic3000 scenarios, modifying the device in question. In this manner, all 1,782 participants received two smartphone questions, while 159 participants received at least one of these five Cubetastic3000 misbehavior questions. Across all participants, the VUR was 46.7\% (of 1,782) for smartphones, whereas the VUR increased to 58.8\% (of 159) for same misbehaviors on the Cubetastic3000. The VURs for both devices for these questions are in Table \ref{deviceVUR}.
%
%To ensure independence of observations, we performed a Mann-Whitney U test to compare participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants). This difference is statistically significant ($U=108,664.0$ with $p<0.0005$) but the effect size is very small ($r=0.08$). Because of this, we did not further reduce our statistical power by separately comparing the five misbehaviors. We conclude that users are likely more wary of misbehaviors on wearables than smartphones, but this difference is likely negligible. The entire effect may be due to participants' familiarity with smartphones, and therefore this effect may disappear as they increasingly encounter more wearables.
